---
title: "Descriptive Stat for GREG Student Survey 1"
author: "Maggie Wu"
date: "June 7, 2018"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

55.73% people had 3-5 group exam experience and only 3.16% student never took group exam before.


```{r, echo=FALSE, warning=FALSE}
Data1 <- read.csv("Data1.csv")
Items<- read.csv("ItemsID1.csv")

library(stringr)
library(ggplot2)
attach(Data1)


sGGbar <- function(v) {
  ##using numbers in Value.Names as labels and values
  stri=deparse(substitute(v))
  label1 <- Items$Value.Names[Items$ColName==stri]
  label1 = as.character(label1)
  label1<-as.list(strsplit(label1, ";"))
  label1<-unlist(label1)
  length1=length(label1)

  ns = " "
  for (i in 1:length1) {
     if(duplicated(label1)[i]==TRUE){
      label1[i] = ns
       ns = paste(" ", ns, sep=" ")
    }
  }
  
  #If the value in Value.Names is string, then use the value in Values and use the string in         #Values.Names as labels
  argm = Items$Values[Items$ColName==stri]
  argm = as.character(argm)
  argm<-as.list(strsplit(argm, ","))
  argm<-unlist(argm)
  argm = as.numeric(argm)
  ##data frame 
  freq<-table(factor(v, levels = min(argm):max(argm)))
  freq<-as.vector(freq)
  DF <- data.frame(Frequency = freq,
                  Values = gl(length1, 1, labels = label1))

  head <- Items$Stem[Items$ColName==stri]
  head<- as.character(head)
  head <-paste0(strwrap(head, width=40), collapse="\n")
  #plot data
  gp<-ggplot(DF, aes(x = Values, y = Frequency)) +
  xlab("") + ylab("Frequency") +
  expand_limits(y = c(0, max(DF$Frequency)*1.1)) + 
  geom_bar(stat = "identity", fill = "#56B4E9") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_text(aes(label = sprintf("%.2f%%", Frequency/sum(Frequency) * 100)), 
            vjust = -.5) +
  labs(title=head)
  print(gp+theme(plot.title = element_text(size = rel(1.2), hjust = 0.5, face = "bold")))
}

 sGGbar2 <- function(v) {
  stri=deparse(substitute(v))
  label1 <- Items$Value.Names[Items$ColName==stri]
  label1 = as.character(label1)
  label1<-as.list(strsplit(label1, ";"))
  label1<-unlist(label1)
  length1=length(label1)

  ns = " "
  for (i in 1:length1) {
     if(duplicated(label1)[i]==TRUE){
      label1[i] = ns
       ns = paste(" ", ns, sep=" ")
     }else{
      label1=label1
    }
  }
  
  argm =as.numeric(label1)
  
  if(anyNA(argm)){
    argm = Items$Values[Items$ColName==stri]
    argm = as.character(argm)
    argm<-as.list(strsplit(argm, ","))
    argm<-unlist(argm)
    argm = as.numeric(argm)
  }
  
  freq<-table(factor(v, levels = min(argm):max(argm)))
  freq<-as.vector(freq)
  DF <- data.frame(Frequency = freq,
                  Values = gl(length1, 1, labels = label1))

  head <- Items$Wording[Items$ColName==stri]
  head<- as.character(head)
  head <-paste0(strwrap(head, width=50), collapse="\n")
  
  gp<-ggplot(DF, aes(x = Values, y = Frequency)) +
  xlab("") + ylab("Frequency") +
  expand_limits(y = c(0, max(DF$Frequency)*1.1)) + 
  geom_bar(stat = "identity", fill = "#56B4E9") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_text(aes(label = sprintf("%.2f%%", Frequency/sum(Frequency) * 100)), 
            vjust = -.5) +
  labs(title=head)
  print(gp+theme(plot.title = element_text(size = rel(1.2), hjust = 0.5, face = "bold")))

}
sHIST <- function(v) {

  m=round(mean(v, na.rm = TRUE),2)
  m=toString(m)
  sdt=round(sd(v, na.rm = TRUE),2)
  sdt = toString(sdt)
  mands=paste(c(m,sdt),collapse = "/")
  ad <- paste(c("M(SD)", mands), collapse = "=")
  
  med = round(median(v, na.rm = TRUE),2)
  med = toString(med)
  ad2 <- paste(c("Med", med), collapse = "=")
  
  stri=deparse(substitute(v))
  head <- Items$Wording[Items$ColName==stri]
  head<- as.character(head)
  head <-paste0(strwrap(c(head,ad,ad2), width=40), collapse="\n")
  
  
  gp<-ggplot(data=Data1, aes(x = v)) +
     geom_histogram(breaks=seq(0, 100, by = 10),
                 col="#000000",
                 fill="#56B4E9") +
  labs(title = head) +
  labs(x="0-100%", y="Frequency")

  print(gp+theme(plot.title = element_text(size = rel(1.2), hjust = 0.5, face = "bold")))
}



BN<-sGGbar(Before.N)


```

Among those students who had group exam experience before, over 50% students enjoyed the group exam. "SGSB" refers to "Some Good, Some Bad" in the graph.

```{r, echo=FALSE, warning=FALSE}

BG<-sGGbar(Before.Good)

```

Most Groups are formed by 3 students. 

```{r, echo=FALSE, warning=FALSE}
GN<-sGGbar(G.N)
```

##Preparation

```{r, echo=FALSE, warning=FALSE}
Dis<-sGGbar(Discuss)
```
```{r, echo=FALSE, warning=FALSE}
Study1<-sHIST(Study_1)
Study2<-sHIST(Study_2)
Study3<-sHIST(Study_3)
Study4<-sHIST(Study_4)
```


##Observation
```{r, echo=FALSE, warning=FALSE}
P1<-sHIST(Parti_1)
P2<-sHIST(Parti_2)
P3<-sHIST(Parti_3)
P4<-sHIST(Parti_4)
P5<-sHIST(Parti_5)
```
```{r, echo=FALSE, warning=FALSE}
K1<-sGGbar2(Know_1)
K2<-sGGbar2(Know_2)
K3<-sGGbar2(Know_3)
K4<-sGGbar2(Know_4)

```


##Decision

How were group decisions made
```{r, echo=FALSE, warning=FALSE}
D1<-sHIST(Decide_1)
D2<-sHIST(Decide_2)
D3<-sHIST(Decide_3)
D4<-sHIST(Decide_4)
```

```{r, echo=FALSE, warning=FALSE}

pace<-sGGbar(Pace)
```



##Group Experience
Please rate how true the following statements are about your group experience . . .
 
```{r, echo=FALSE, warning=FALSE}
GE11<-sGGbar2(G.Exp1_1)
GE12<-sGGbar2(G.Exp1_2)
GE13<-sGGbar2(G.Exp1_3)

GE21<-sGGbar2(G.Exp2_1)
GE22<-sGGbar2(G.Exp2_2)
GE23<-sGGbar2(G.Exp2_3)
GE24<-sGGbar2(G.Exp2_4)

GE31<-sGGbar2(G.Exp3_1)
GE32<-sGGbar2(G.Exp3_2)

GE33<-sGGbar2(G.Exp3_3)

```


```{r, echo=FALSE, warning=FALSE}
NAG<-sGGbar(NotAgain)
```


##Future
```{r, echo=FALSE, warning=FALSE}
mid<-sGGbar(Recc.Mid)
```

```{r, echo=FALSE, warning=FALSE}
fin<-sGGbar(Recc.Final)
```