---
title: "Descriptive Stat for GREG Student Survey 2"
author: "Maggie Wu"
date: "June 25, 2018"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r, echo=FALSE, warning=FALSE}


Data2 <- read.csv("Data2.csv")
Items2<- read.csv("Items2.csv")

library(stringr)
library(ggplot2)
attach(Data2)



sGGbar <- function(v) {
  
  stri=deparse(substitute(v))
  label1 <- Items2$Value.Names[Items2$ColName==stri]
  label1 = as.character(label1)
  label1<-as.list(strsplit(label1, ";"))
  label1<-unlist(label1)
  length1=length(label1)

  ns = " "
  for (i in 1:length1) {
     if(duplicated(label1)[i]==TRUE){
      label1[i] = ns
       ns = paste(" ", ns, collapse = "")
     }
  }
  
  argm =as.numeric(label1)
  
  if(anyNA(argm)){
    argm = Items2$Values[Items2$ColName==stri]
    argm = as.character(argm)
    argm<-as.list(strsplit(argm, ","))
    argm<-unlist(argm)
    argm = as.numeric(argm)
  }
  
  
  
  
  freq<-table(factor(v, levels = min(argm):max(argm)))
  freq<-as.vector(freq)
  DF <- data.frame(Frequency = freq,
                  Values = gl(length1, 1, labels = label1))

  head <- Items2$Stem[Items2$ColName==stri]
  head<- as.character(head)
  head <-paste0(strwrap(head, width=40), collapse="\n")
  
  gp<-ggplot(DF, aes(x = Values, y = Frequency)) +
  xlab("") + ylab("Frequency") +
  expand_limits(y = c(0, max(DF$Frequency)*1.1)) + 
  geom_bar(stat = "identity", fill = "#56B4E9") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_text(aes(label = sprintf("%.2f%%", Frequency/sum(Frequency) * 100)), 
            vjust = -.5) +
  labs(title=head)
  print(gp+theme(plot.title = element_text(size = rel(1.2), hjust = 0.5, face = "bold")))
}

sGGbar2 <- function(v) {
  
  stri=deparse(substitute(v))
  label1 <- Items2$Value.Names[Items2$ColName==stri]
  label1 = as.character(label1)
  label1<-as.list(strsplit(label1, ";"))
  label1<-unlist(label1)
  length1=length(label1)

  ns = " "
  for (i in 1:length1) {
     if(duplicated(label1)[i]==TRUE){
      label1[i] = ns
       ns = paste(" ", ns, sep=" ")
    }
  }
  
  argm =as.numeric(label1)
  
  if(anyNA(argm)){
    argm = Items2$Values[Items2$ColName==stri]
    argm = as.character(argm)
    argm<-as.list(strsplit(argm, ","))
    argm<-unlist(argm)
    argm = as.numeric(argm)
  }
  
  freq<-table(factor(v, levels = min(argm):max(argm)))
  freq<-as.vector(freq)
  DF <- data.frame(Frequency = freq,
                  Values = gl(length1, 1, labels = label1))

  head <- Items2$Wording[Items2$ColName==stri]
  head<- as.character(head)
  head <-paste0(strwrap(head, width=40), collapse="\n")
  
  gp<-ggplot(DF, aes(x = Values, y = Frequency)) +
  xlab("") + ylab("Frequency") +
  expand_limits(y = c(0, max(DF$Frequency)*1.1)) + 
  geom_bar(stat = "identity", fill = "#56B4E9") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_text(aes(label = sprintf("%.2f%%", Frequency/sum(Frequency) * 100)), 
            vjust = -.5) +
  labs(title=head)
  print(gp+theme(plot.title = element_text(size = rel(1.2), hjust = 0.5, face = "bold")))
}

sHIST <- function(v) {

  m=round(mean(v, na.rm = TRUE),2)
  m=toString(m)
  sdt=round(sd(v, na.rm = TRUE),2)
  sdt = toString(sdt)
  mands=paste(c(m,sdt),collapse = "/")
  ad <- paste(c("M(SD)", mands), collapse = "=")
  
  med = round(median(v, na.rm = TRUE),2)
  med = toString(med)
  ad2 <- paste(c("Med", med), collapse = "=")
  
  stri=deparse(substitute(v))
  head <- Items2$Wording[Items2$ColName==stri]
  head<- as.character(head)
  head <-paste0(strwrap(c(head,ad,ad2), width=40), collapse="\n")
  
  vec<-0:100
  toString(vec)
  vec<-as.character(vec)
  vec<-as.list(strsplit(vec, ","))
  vec<-unlist(vec)
  length1=length(vec)
  
  freq<-table(factor(v, levels = 0:100))
  freq<-as.vector(freq)
  DF <- data.frame(Frequency = freq,
                  Values = vec)
  
  gp<-ggplot(Data2, aes(x = v)) +
     geom_histogram(breaks=seq(0, 100, by = 10),
                 col="#000000",
                 fill="#56B4E9") +
  labs(title = head) +
  labs(x="0-100%", y="Frequency")

  print(gp+theme(plot.title = element_text(size = rel(1.2), hjust = 0.5, face = "bold")))

}



GN<-sGGbar(G.N)

```

##For Midterm 2, how did you form your group?
```{r, echo=FALSE, warning=FALSE}
GFORM<-sGGbar(GForm)

```

##Before this exam, how much did you and your group discuss HOW you would work together: make decisions, resolve conflicts, etc.
```{r, echo=FALSE, warning=FALSE}
discuss<-sGGbar(Discuss)
```

##Fill in the boxes with the percentage of time for how you studied for this exam.
(Answers should sum to 100%)
```{r, echo=FALSE, warning=FALSE}
Study1<-sHIST(Study_1)
Study2<-sHIST(Study_2)
Study3<-sHIST(Study_3)
Study4<-sHIST(Study_4)
```


##During the group exam, how much did each member participate in the work? 
(Answers should sum to 100%)
```{r, echo=FALSE, warning=FALSE}
P1<-sHIST(Parti_1)
P2<-sHIST(Parti_2)
P3<-sHIST(Parti_3)

P4<-sHIST(Parti_4)
P5<-sHIST(Parti_5)
```

##How well do you know each person in your group? 
(Please reference members in the same order as you did above.)
```{r, echo=FALSE, warning=FALSE}
K1<-sGGbar2(Know_1)
K2<-sGGbar2(Know_2)
K3<-sGGbar2(Know_3)
```

##How were group decisions made? 
(Choices should sum to 100%)
```{r, echo=FALSE, warning=FALSE}
D1<-sHIST(Decide_1)
D2<-sHIST(Decide_2)
D3<-sHIST(Decide_3)
d4<-sHIST(Decide_4)
```

##How was the pace of the group work together, for you?
```{r, echo=FALSE, warning=FALSE}
Pace<-Data2$Pace
pace<-sGGbar(Pace)
```


##Please rate how true the following statements are about how your group worked together
```{r, echo=FALSE, warning=FALSE}
GE11<-sGGbar2(G.Exp1_1)
GE12<-sGGbar2(G.Exp1_2)
GE13<-sGGbar2(G.Exp1_3)
GE21<-sGGbar2(G.Exp2_1)
GE22<-sGGbar2(G.Exp2_2)
GE23<-sGGbar2(G.Exp2_3)
GE24<-sGGbar2(G.Exp2_4)
GE25<-sGGbar2(G.Exp2_5)
GE34<-sGGbar2(G.Exp3_4)
GE35<-sGGbar2(G.Exp3_5)
GE37<-sGGbar2(G.Exp3_7)
GE38<-sGGbar2(G.Exp3_8)
```

##Was there one or more people in your group who you prefer not to work with again?
```{r, echo=FALSE, warning=FALSE}
NAG<-sGGbar(NotAgain)
```


##During this group exam, I felt comfortable sharing my answer with the group...
```{r, echo=FALSE, warning=FALSE}
S2<-sGGbar2(Share_2)
S3<-sGGbar2(Share_3)
S6<-sGGbar2(Share_6)
S4<-sGGbar2(Share_4)
```

##For which midterm (MT) was the experience of working with your group better?
```{r, echo=FALSE, warning=FALSE}
better<-sGGbar2(Better_3)
```

##Did you change how you prepared for or participated in THIS GROUP EXAM as compared to the group exam in MIDTERM 1?
```{r, echo=FALSE, warning=FALSE}
change<-sGGbar(Change)
```


##I see myself as . . .
```{r, echo=FALSE, warning=FALSE}
T1<-sGGbar2(TIPI_1)
T2<-sGGbar2(TIPI_2)
T3<-sGGbar2(TIPI_3)
T4<-sGGbar2(TIPI_4)
T5<-sGGbar2(TIPI_5)
```

##Click to write the question text
```{r, echo=FALSE, warning=FALSE}
q1<-sGGbar2(Q66_1)
q2<-sGGbar2(Q66_2)
q3<-sGGbar2(Q66_3)
q4<-sGGbar2(Q66_4)
q5<-sGGbar2(Q66_5)
```